Journey: A Study of Scalabilty of Memory Management in Linux

### 2017-05-05 paper.tex
Remove a line
Remove some lines

Recent advances in memory technologies are making it possible for machines with
large amounts of memory to become commonplace. Many current systems already
have dozens or hundreds of gigabytes of memory. These technology advances can
enable systems with terabytes of memory in the not very distant future. For
example, non-volatile memory technologies, which have denser physical
structures than traditional DRAM are making such large memories available and
more accessible \cite{xpoint}.

@@

To determine which pages to swap out, Linux uses the Page Frame Reclamation
subsystem. Choosing which pages to swap out is important because if the system
swaps out pages that are about to be used, thrashing may be induced, in which
the system wastes lots of time swapping out a page just swap it back in.

@@

The PFRA runs primarily as a kernel thread called kswapd. kswapd runs at regular
intervals and sleeps in between. Also, it may be invoked if the system detects
that memory has gone below a threshold. kswapd will continue to run until enough
pages are freed to bring the free memory pool above some threashold. Then,
kswapd goes back to sleep \cite{utlk}.  One concern with systems that have a large memory
usage is that kswapd may expend significant CPU time scanning through hundreds
of thousands of pages.

>>>>

Recent advances in memory technologies are making it possible for machines with
large amounts of memory to become commonplace.
These technology advances can
enable systems with terabytes of memory in the not very distant future. For
example, non-volatile memory technologies, which have denser physical
structures than traditional DRAM are making such large memories available and
more accessible \cite{xpoint}.

@@

To determine which pages to swap out, Linux uses the Page Frame Reclamation
subsystem. Choosing which pages to swap out is important because if the system
swaps out pages that are about to be used, thrashing may be induced.

@@

The PFRA runs primarily as a kernel thread called kswapd. kswapd runs at regular
intervals and sleeps in between. Also, it may be invoked if the system detects
that memory has gone below a threshold. kswapd will continue to run until enough
pages are freed to bring the free memory pool above some threshold before going to
sleep \cite{utlk}.  One concern with systems that have a large memory
usage is that kswapd may expend significant CPU time scanning through hundreds
of thousands of pages.
